---
title: "Penguins ANOVA"
author: "Lauren Jack"
date: "11/6/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)

```

```{r}
library(car)
library(onewaytests)
```

Our Questions:
Is there a significant distance in mean flipper length for female penguins by species (chinstrap, Gentoo, and Adelie)?


2.) Do some exploring, knowing that the data is already in tidy format

Few Functions: width + table for easy counting over multiple factors

Update the species name using case_when

```{r}
penguins <- read_csv('penguins.csv')

counts <- with(penguins, table(species, sex))

penguins2 <- penguins %>% 
  mutate(common_name =
           case_when(
             species == "Chinstrap penguin (Pygoscelis antarctica)" ~ "Chinstrap",
             species == "Gentoo penguin (Pygoscelis papua)" ~ "Gentoo",
             species == "Adelie Penguin (Pygoscelis adeliae)" ~ "Adelie"
               
           )
         ) %>% 
  select(-species) %>% 
  filter(sex == "FEMALE")
```


```{r}
hists <- ggplot(penguins2, aes(x = flipper_length)) +
  geom_histogram(aes(fill = common_name)) +
  facet_wrap(~common_name)

hists
```


```{r}
QQ_Peng <- ggplot(penguins2, aes(sample = flipper_length)) +
  geom_qq() +
  facet_wrap(~ common_name)

QQ_Peng
```

#Levenne's test for equal variences (> 2 groups ... if you have two groups, use the F-Test for equal variences)

#We'll use the function leveneTest from the 'car' packages

# HNull: Variances are Equal
# H Alt: Variances are unequal

```{r}
penguins_levenne <- leveneTest(flipper_length ~ common_name, data = penguins2)

penguins_levenne

#We retain the null hypothesis of equal variences (p = 0.06)

penguins_var <-penguins2 %>% 
  group_by(common_name) %>% 
  summarize(
    variance = var(flipper_length)
  )

penguins_var

```

